The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-02-20 src/ms.tex
Performance section

\subsection*{Future} \label{sec:core-features-future}

>>>>

As features are added and corner cases dealt with, performance often
suffers.  Hence, pull requests that improve performance are welcomed
generally, and were even the main goal for one release cycle.  For
most packages, this meant improvements in the \python\ code, but for
some the most time-critical pieces were rewritten in~C (e.g., for
convolution of images, sigma-clipping, and converting time strings to
binary).  Furthermore, a particular effort was made to ensure
\astropypkg\ is thread-safe, so that it can be used on supercomputer
clusters.

% \subsection*{Future} \label{sec:core-features-future}
% MHvK: Merged with the new feature section
